He Said What Now?!: Predicting Interest in the Term *China Virus* by State

### 2020-05-06 Final-Draft.Rmd
more proofing

## 4.5 Are our models strong?: Prediction & classification summaries

@@

### 5.1a 
```{r, message=FALSE, include=FALSE}
#Repeated Measures
set.seed(454)
pred_1 <- posterior_predict(
  RM_model,
  newdata = model_data, transform = TRUE)

sum1<-prediction_summary(y = model_data$ChinaVirusInterest,
  yrep = pred_1)
```

### 5.1b
```{r, message=FALSE, include=FALSE}
#Normal Regression
set.seed(454)
pred_2 <- posterior_predict(
  NR_model,
  newdata = model_data, transform = TRUE)

sum2<-prediction_summary(y = model_data$ChinaVirusInterest,
  yrep = pred_2)
```

### 5.1c
```{r, message=FALSE, include=FALSE}
#Repeated Measures + Normal Regression
set.seed(454)
pred_3 <- posterior_predict(
  model_3,
  newdata = model_data, transform = TRUE)

sum3<-prediction_summary(y = model_data$ChinaVirusInterest,
  yrep = pred_3)
```

### 5.1d
```{r message=FALSE, include=FALSE}
#Longitudinal Model
set.seed(454)
pred_4 <- posterior_predict(
  complexmod,
  newdata = model_data, transform = TRUE)

@@

## 5.3 Final Model

>>>>

@@

```{r, message=FALSE, include=FALSE}
#Repeated Measures
set.seed(454)
pred_1 <- posterior_predict(
  RM_model,
  newdata = model_data, transform = TRUE)

sum1<-prediction_summary(y = model_data$ChinaVirusInterest,
  yrep = pred_1)

#Normal Regression
set.seed(454)
pred_2 <- posterior_predict(
  NR_model,
  newdata = model_data, transform = TRUE)

sum2<-prediction_summary(y = model_data$ChinaVirusInterest,
  yrep = pred_2)

#Repeated Measures + Normal Regression
set.seed(454)
pred_3 <- posterior_predict(
  model_3,
  newdata = model_data, transform = TRUE)

sum3<-prediction_summary(y = model_data$ChinaVirusInterest,
  yrep = pred_3)

#Longitudinal Model
set.seed(454)
pred_4 <- posterior_predict(
  complexmod,
  newdata = model_data, transform = TRUE)

@@

## 5.4 Final Model
